Intro Seminar

### 2017-03-01 doc/seminar2017.Rmd
Changed box plots to slides theme

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

# Boxplot of ACR in uVDBP categories
dsBase %>% 
  select(UDBPStatus, ACR) %>% 
  na.omit() %>% 
  box_plot("UDBPStatus", "log(ACR)",
           "Urinary VDBP status",
           "log Urine ACR (mg/mmol)")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFR_status, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot2("eGFR_status", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine")

@@

>>>>

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_slides("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFRStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_slides("eGFRStatus", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine")

@@

## Glycemic Status

```{r DM boxplot}

# Boxplot of uVDBP concentrations across DM categories

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(dmStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_slides("dmStatus", "log(udbpCrRatio)", 
            "Glycemic Status",
            "log uVDBP:Creatinine")
